### 2019-11-14 thesis/txt/1-related-work.tex
write about last ci papers, fix references

~\cite{holck2003continuous}

~\cite{schermann2016towards}

~\cite{hilton2017trade-offs}

~\cite{hilton2016usage}

@@

BART (2019) Jenkins-Plugin. https://plugins.jenkins.io/bart. Accessed: 2019-07-24

>>>>

Hilton et al.~\cite{hilton2017trade-offs} investigate the motivations of developers to use CI through several surveys.
Developers use CI to ensure consistency and quality across different execution environments and increase confidence into the code they deploy.

Hilton et al.~\cite{hilton2016usage} analyze how and why open source projects use CI.
They observe CI usage in a broad range of projects, it supports them to catch bugs earlier and have more confidence in a successful build and shorten release cycles.

@@

### 2019-11-14 thesis/txt/3-data-set.tex
write about last ci papers, fix references

\paragraph{Example Set}
Our data set is organized in example sets. One example set always contains build log in/output examples from the same software repository or project and for one specific build log information. They are all from one repository because we investigate information retrieval techniques which are always configured to the scope of one particular software repository or project.
Each example set has an identifying \emph{save name}, a \emph{build log information} that is desired to be extracted by this configuration, and a list of \emph{in / output examples}.

@@

\subsubsection{Results}
In total we sent out mails to 246 developers, asking about 3.2 build logs on average.
32 of these mails could not be delivered, e.g.\ because they were addressed at noreply mail addresses.
These 32 mails related to 68 of the build logs.
We received answers from 61 developers, responding about 144 build logs.
The proportions of mails and logs answered about, not delivered and unanswered is shown in Figure~\ref{fig:mails-answers-received-mails} and Figure~\ref{fig: mails-answers-received-builds}.

>>>>

\paragraph{Example Set}
\label{sec:example-set}
Our data set is organized in example sets. One example set always contains build log in/output examples from the same software repository or project and for one specific build log information. They are all from one repository because we investigate information retrieval techniques which are always configured to the scope of one particular software repository or project.
Each example set has an identifying \emph{save name}, a \emph{build log information} that is desired to be extracted by this configuration, and a list of \emph{in / output examples}.

@@

\subsubsection{Results}
In total we sent out mails to 246 developers, asking about 3.2 build logs on average.
32 of these mails could not be delivered, e.g.\ because they were addressed at noreply mail addresses.
These 32 mails related to 68 of the build logs.
We received answers from 61 developers, responding about 144 build logs.
The proportions of mails and logs answered about, not delivered and unanswered is shown in Figure~\ref{fig:mails-answers-received-mails} and Figure~\ref{fig:mails-answers-received-builds}.
